---
title: "Pink Tax Spain"
author: "Phong Duong, Nienke Visscher"
date: "2024-02-15"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Library

```{r}
library(xml2)
library(tidyverse)
library(RSelenium)
library(glue)
library(magrittr)
```

## Mercadona

```{r}
set_config(
  user_agent("Mozilla/5.0 (Windows NT 10.0; Win64; x64) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/121.0.0.0 Safari/537.36; Nienke Visscher / nienvis@gmail.com")
)

#Code for attaching JAVA
#Sys.getenv("JAVA_HOME")
#Sys.setenv(JAVA_HOME = "C:/Program Files/Common Files/Oracle/Java/javapath/java.exe")
#Sys.getenv("PATH")
#install.packages("RSelenium", dependencies = TRUE)

#Opening hidden browser
remDr <- rsDriver(port = 4462L, browser = "firefox",  verbose=F, chromever = NULL)


merc <-"https://tienda.mercadona.es/categories"

browseURL(prep_browser(merc))
 
remDr$client$navigate(merc)


```

```{r}

driver <- remDr$client

#Note following only when having newly initiated the port
#Accepting cookies
driver$findElement(value = "(//button[@class = 'ui-button ui-button--small ui-button--tertiary ui-button--positive'])[1]")$clickElement()

#Click on text box
driver$findElement(value = "(//input[@class = 'ym-hide-content'])[1]")$clickElement()

#Define findElement of the textbox
codigo <-driver$findElement(value = "(//input[@class = 'ym-hide-content'])[1]")

#Fill in the text box
codigo$sendKeysToElement(list("28014"))

#Click 
driver$findElement(value = "(//button[@class = 'button button-primary button-big'])[1]")$clickElement()

##### Until here


#Insert below
cat_name <- cat_html |> 
   xml_find_all("//label[@class='subhead1-r']") |>
   xml_text()


#Get URL first categories
url <- list()
  
driver$findElement(value = "(//label[@class='subhead1-r' and contains(text(), 'Cuidado del cabello')])[1]")$clickElement()

Sys.sleep(1)

url[1] <-driver$getCurrentUrl()


for (i in (2:4)){
  
  driver$findElement(value = "(//button[@class = 'ui-button ui-button--big ui-button--secondary ui-button--positive category-detail__next-subcategory'])[1]")$clickElement()
  
Sys.sleep(1)
  
  url[i] <-driver$getCurrentUrl()
  
  
}

#Get URL second categories
  
driver$findElement(value = "(//label[@class='subhead1-r' and contains(text(), 'Cuidado facial y corporal')])[1]")$clickElement()

Sys.sleep(1)

url[5] <-driver$getCurrentUrl()



for (i in (6:15)){
  
  
  driver$findElement(value = "(//button[@class = 'ui-button ui-button--big ui-button--secondary ui-button--positive category-detail__next-subcategory'])[1]")$clickElement()
  
  Sys.sleep(1)
  
  url[i] <-driver$getCurrentUrl()
  
}


url <-unlist(url)


```

```{r}


cat_grabber <- function(url){
  

driver$navigate(url)
  
Sys.sleep(1)

cat_html <-driver$getPageSource()[[1]] |>
  read_html() 

cat_info <- cat_html|> 
    xml_find_all("//*[@id='root']//button/div[2]") |>
    xml_text()

subcat_name <- cat_html |> 
   xml_find_all("//h1[@class='category-detail__title title1-b']") |>
   xml_text()


cat_clean<-cat_info|> 
  str_replace_all("\\€ |/|\\.|!", "") |>
  str_replace_all("\\€\\d+,\\d+", "") |>
  str_replace_all("(?<=\\d\\s)ml", "/ml/") |> 
  str_replace_all("(?<=\\d\\s)ud", "/ud/") |> 
  str_replace_all("(?<=\\d\\s{0,2})ud", "/ud/") |> 
  str_replace_all("(?<=\\d\\s)L", "/L/") |> 
  str_replace_all("(?<=\\d\\s)tarro", "") |> 
  str_replace_all("(?<=\\d\\s)g\\s", "/g/") |> 
  str_replace_all("(?<=\\d\\s)sobres", "/sobres/") |> 
  str_replace_all("(?<=\\d\\s)bandas", "/bandas/") |> 
  str_replace_all("(?<=sensibleCaja\\s)1", "/") |> 
  str_replace_all("(?<=DovePaquete\\s)4", "/") |> 
  str_replace_all("ud.(?=\\s*\\()", "") |> 
  str_replace_all("\\s(?=\\d+\\s*/)", "/") |> 
  str_replace_all("(?<=[[:lower:]])(?=[[:digit:]])", "/") |> 
  str_replace_all("\\(|\\)", "") |> 
  str_replace_all("\\.", "")|> 
  strsplit("/")


cat_clean <- lapply(cat_clean, function(x) {
  length(x) <- 5
  x
})


cat_clean<- cat_clean[lengths(cat_clean) <= 5]

data.frame(
  name = sapply(cat_clean, `[`, 1),
  quantity = sapply(cat_clean, `[`, 2),
  quantity_unit = sapply(cat_clean, `[`, 3),
  price = sapply(cat_clean, `[`, 4),
  ud =  sapply(cat_clean, `[`, 5),
  subcat =  sapply(subcat_name, `[`, 1),
  stringsAsFactors = FALSE
)


}

cat_grabber(url)


final <- map_dfr(url, cat_grabber) 

```

### Data Collection

```{r}
driver <- rsDriver(browser = "firefox",
                   chromever = NULL,
                   verbose = F)

remDr <- driver[["client"]]
```

#### Main Webpage

```{r}
clarel_url <- "https://www.clarel.es/es/"

remDr$navigate(clarel_url)

Sys.sleep(4)

#Reject cookie
remDr$findElement(using = "xpath", "//button[contains(@class, 'info_cookie-consent-reject-button')]")$clickElement()
```

#### Scrape Hombre Category

```{r}
get_subcat2_url <- function(category){
  remDr$getPageSource()[[1]] %>% 
    read_html() %>% 
    xml_find_all(glue("//span[a[contains(text(),'{category}')]]//li/a[contains(@class,'item')]")) %>% 
    xml_attr("href") %>% 
    paste0("https://www.clarel.es",.)
}
sub_cat_2_url <- get_subcat2_url("Hombre")

remDr$navigate(sub_cat_2_url[10])
```

```{r}
#Load more items
load_all_items <- function() {
  Sys.sleep(3.5)
  tryCatch(
    {
      suppressMessages({
      load_more_button <-remDr$findElement(using = "xpath", 
                                          "//button[contains(@class, 'load-more-items-button')]")
      while(load_more_button$isElementDisplayed()[[1]]) {
      load_more_button$clickElement()
      Sys.sleep(3.5)
      load_more_button <-remDr$findElement(using = "xpath", 
                                           "//button[contains(@class, 'load-more-items-button')]")
      }
      })
    },
    error = function(e){})
}

# load_all_items()
```

```{r}
#Get all product info
get_product_info <- function(url) {
  remDr$navigate(url)
  
  load_all_items()
  
  paths <- read_html(remDr$getPageSource()[[1]]) %>% 
  xml_find_all("//div[contains(@class, 'box_product-info')]")
  
  get_info <- function(path) {
  brand <- path %>% 
    xml_find_all("div[contains(@class, 'product-featuredbrands')]") %>%
    xml_text()
  
  product_name <- path %>% 
    xml_find_all("a") %>% 
    xml_text()
  
  price <- path %>% 
    xml_find_all("div[contains(@class, 'product-price')]/span[contains(@class,'final-price')]") %>% 
    xml_text()
  
  data.frame(
    brand = brand,
    product_name = product_name,
    price = price
  )
  }
  
  #Get cat & subcats
  cat <- remDr$getPageSource()[[1]] %>% 
    read_html() %>% 
    xml_find_all("//span[@class='subcategory']") %>% 
    xml_text() %>% 
    paste(collapse = "-")
  
  df <- map_dfr(paths, get_info) %>% mutate(full_cat = cat)

  
  return(df)
}


hombre_products <- map_dfr(sub_cat_2_url, get_product_info)

hombre_products
```

#### Scrape Multiple Categories

```{r}
imp_cat <- c("Hombre", "Higiene", "Cabello")

scrape_all <- function(category) {
  remDr$navigate(clarel_url)
  
  subcat2 <- get_subcat2_url(category)
  
  df <- map_dfr(subcat2, get_product_info) 
  
  return(df)
}

start <- Sys.time()
all_products_clarel <- map_dfr(imp_cat ,scrape_all)
stop <- Sys.time()

write_csv(all_products_clarel, "datasets/clarel.csv")
```

### Data Cleaning

```{r}

```{r}
#Quantity detect
cleaned_clarel <- all_products_clarel %>% 
  as_tibble() %>% 
  distinct(product_name, .keep_all = TRUE) %>% 
  separate_wider_delim(full_cat, delim = "-", names = c("category", "sub_category", "product_type")) %>% 
  mutate(qty = str_extract(tolower(product_name), "\\d+ ?ml|\\d+ ?g|\\d+ ?u(ds)?|\\d+(,\\d+)? ?l") ,.after = product_name) %>% 
  mutate(qty = replace_na(qty, "1")) %>% 
  mutate(price = parse_number(str_replace(price, "€", ""), locale = locale(decimal_mark = ","))) %>% 
  mutate(
    avg_price = case_when(
      str_detect(qty, "\\d+ ?ml|\\d+ ?g") ~ price * 100 / as.numeric(str_extract(qty, "\\d+")), #price per 100ml/g
      str_detect(qty, "\\d+ ?u(ds)?") ~ price / as.numeric(str_extract(qty, "\\d+")), #price per unit
      str_detect(qty, "\\d+(,\\d+)? ?l") ~ price *0.1 / parse_number(str_extract(qty, "\\d+(,\\d+)? ?l"), locale = locale(decimal_mark = ",")), #price per 100ml for Litters
      TRUE ~ price 
    )
  ) %>% 
  mutate(avg_price = round(avg_price, 2))
  

cleaned_clarel
```

\
\
